Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-26 PaperBCJ.tex
Final Change

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others, have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to  introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\

>>>>

Technological advances have caused industry transformations; manufacturing, food processing, agricultural industries among others have gone through dramatic changes with the new industrial revolution such as the Precision agriculture(PA)  which has opened a new field for researching  \cite{ortiz2012máquinas}. However, there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times;  while it is true that there are efficient agricultural practices, the lack of technological resources and applications make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer, for the next years it will be planned to  introduce some changes concerning to the innovation to improve production \cite{houtart2014desafio}. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control aspects. 
\\
